Long-range correlations and their event-scale dependence in high-multiplicity pp collisions at $\sqrt{s} = 13$~TeV

### 2020-10-26 sec_ana.tex
updates

Systematic uncertainties on $Y^{\rm{assoc}}$ were estimated by varying the analysis selection criteria and evaluated as functions of $\pttrig$($\ptassoc$) and $\ptlead$ or $\ptjet$ as described in Tab.~\ref{tab:syst}. The uncertainty on $Y^{\rm{assoc}}(\pttrig,\,\ptassoc)$, which denotes the ridge yield as a function of $\pttrig$($\ptassoc$), was evaluated without any biases from even-scale selection. The uncertainties on $Y^{\rm{assoc}}(\ptlead)$ and $Y^{\rm{assoc}}(\ptjet)$, which denote the ridge yield as functions of $\ptlead$ and $\ptjet$, were evaluated only for the 1$<\pttrig, \ptassoc<$2 GeV/$c$ range.

\begin{table}[h!]
\caption{The relative systematic uncertainty of the associated yield spectrum estimated for $Y^{\rm{assoc}}(\pttrig,\,\ptassoc)$, $Y^{\rm{assoc}}(\ptlead)$, and $Y^{\rm{assoc}}(\ptjet)$, respectively.}
\centering
\begin{tabular}{|c|c|c|c|}
\hline 
\multirow{2}{*}{Sources}  & \multicolumn{3}{c|}{Systematic uncertainty (\%)} \\\cline{2-4}
         & $Y^{\rm{assoc}}(\it{p}_{\rm{T, trig}},\,\it{p}_{\rm{T, assoc}})$ & $Y^{\rm{assoc}}(\it{p}_{\rm{T, Lead}})$ & $Y^{\rm{assoc}}(\it{p}_{\rm{T, Jet}})$ \\ \hline \hline
Pileup rejection		& 0.8	&0--4		&0--4		\\ \hline
Primary vertex		& 2.4	&1--12	&1--8		\\ \hline

Tracking			& 4.0 	&2		&2		\\ \hline

ZYAM			& 5.1	&2		&2		\\ \hline
Jet contamination	& 4.5	&3--7		&3--9		\\ \hline

Event mixing			& 4.4	&2--8		&1--16	\\ \hline

Efficiency correction	& 2.5 	&1		&1		\\ \hline \hline
Total(in quadrature)			& 9.7	&4--16	&4--22	\\ 
\hline 
\end{tabular}
\label{tab:syst}
\end{table}

The uncertainty from the pileup rejection is estimated by measuring the changes of results with different rejection criteria from the default one. The pileup rejection is achieved by reconstructing the multiple vertice in the individual event. The multiplicity of the reconstructed vertice determines whether the event is contaminated by pileup or not. The variation is set by the minimum multiplicity of reconstructed vertices from 5 to 3. 
%Pileup cut (multbins) -> (default pileup from the physics selection)
%Pileup cut (multbins) -> PileupMV (?)
The estimated uncertainty is 1\% without $\ptlead$ or $\ptjet$ selection. The uncertainty varies up to 4\% for event with the $\ptlead$ or $\ptjet$ selection. The uncertainty from the primary vertex selection along the beam axis is estimated by varying the selection range of primary vertex from $|z_\mathrm{vtx}|<$ 8 to 6 cm. The narrower primary vertex selection allows one to test the acceptance effect on the measurement. The estimated uncertainty is 1--12\% with the varying event-scale selections.

The uncertainty from the track selection is estimated by varying from the hybrid tracks to the other one optimized for particle identification that is called the global tracks. The selection criteria of the global tracks are almost identical to the hybrid tracks except for the requirement of at least one hit on the SPD. Due to the requirement, the quality of the global tracks is sensitive to the condition of the SPD, finally resulting a non-flat azimuthal distribution of charged particles with the selection.     
%The variation is achieved by changing the mandatory SPD requirement and the maximal threshold for chi-square of the track fit.
%https://github.com/alisw/AliRoot/blob/master/ANALYSIS/ESDfilter/macros/AddTaskESDFilter.C
The uncertainty origination from the variation of the track selections is estimated as 4\%. The uncertainty is measured by averaging for various transverse momentum ranges regardless of event-scale selections.

The ZYAM procedure is implemented by finding a minimum yield in a given finding range. The uncertainty from the ZYAM procedure is estimated by varying the range from the $|\Delta\varphi|<\pi/$2 up to $|\Delta\varphi|<1.2$. The estimated uncertainty for track selection is 5.1\% by averaging the uncertainty for the whole transverse momentum bins and 2\% for 1$<\it{p}_{\rm{T}}<$2 GeV/$c$ tracks, which is not largely affected by the event-scale selection. The uncertainty from the jet contamination is estimated by varying the $\Delta\eta$ projection range to see how much the jet contamination varies, which is thought be small. The estimated uncertainty is 3--9\% with the varying event-scale selection.

The uncertainty from the event mixing intervals of primary vertex is estimated by varying the interval size from 2 to 1 cm. The estimated uncertainty is 1--16\% with the varying event-scale selection. The uncertainty from the efficiency correction for charged track is estimated by comparing correlations functions of true particles with correlations functions of reconstructed tracks with the efficiency correction in simulation. The estimated uncertainty is 1-2.5\% regardless of the event-scale selection.

>>>>

Systematic uncertainties on $Y^{\rm{assoc}}$ and $Y^{\rm{jet}}$ were estimated by varying the analysis selection criteria and evaluated as functions of $\pttrig$($\ptassoc$) and $\ptlead$ or $\ptjet$ as described in Tab.~\ref{tab:syst}. The uncertainty on $Y^{\rm{assoc}}(\pttrig,\,\ptassoc)$, which denotes the ridge yield as a function of $\pttrig$($\ptassoc$), was evaluated without any biases from even-scale selection. The uncertainties on $Y^{\rm{assoc}}(\ptlead)$ and $Y^{\rm{assoc}}(\ptjet)$, which denote the ridge yield as functions of $\ptlead$ and $\ptjet$, were evaluated for the 1$<\pttrig, \ptassoc<$2 GeV/$c$ range with event-scale selections using $\ptlead$ or $\ptjet$. The uncertainties on $Y^{\rm{jet}}(\ptlead)$ and $Y^{\rm{jet}}(\ptjet)$ were evaluated and described together because the measured uncertainties are comparable each other.

\begin{table}[h!]
\caption{The relative systematic uncertainty of the associated yield spectrum estimated for $Y^{\rm{assoc}}(\pttrig,\,\ptassoc)$, $Y^{\rm{assoc}}(\ptlead)$, $Y^{\rm{assoc}}(\ptjet)$, and $Y^{\rm{jet}}$ respectively.}
\centering
\begin{tabular}{|c|c|c|c|c|}
\hline 
\multirow{2}{*}{Sources}  & \multicolumn{4}{c|}{Systematic uncertainty (\%)} \\\cline{2-5} 
         & $Y^{\rm{assoc}}(\it{p}_{\rm{T, trig}},\,\it{p}_{\rm{T, assoc}})$ & $Y^{\rm{assoc}}(\it{p}_{\rm{T, Lead}})$ & $Y^{\rm{assoc}}(\it{p}_{\rm{T, Jet}})$ & $Y^{\rm{jet}}$ \\ \hline \hline
Pileup rejection		& 0.8	&0--4		&0--4	&0--2	\\ \hline
Primary vertex		& 2.4	&1--12	&1--8	&1--8	\\ \hline

Tracking			& 4.0 	&2		&2	&2--3	\\ \hline

ZYAM			& 5.1	&2		&2	&N.A.	\\ \hline
Jet contamination	& 4.5	&3--7		&3--9	&N.A.	\\ \hline

Event mixing			& 4.4	&2--8		&1--16	&1	\\ \hline

Efficiency correction	& 2.5 	&1		&1	&3	\\ \hline \hline
Total(in quadrature)			& 9.7	&4--16	&4--22	&4--10 \\ 
\hline 
\end{tabular}
\label{tab:syst}
\end{table}

The uncertainty from the pileup rejection is estimated by measuring the changes of results with different rejection criteria from the default one. The pileup rejection is achieved by reconstructing the multiple vertice in the individual event. The multiplicity of the reconstructed vertice determines whether the event is contaminated by pileup or not. The variation is set by the minimum multiplicity of reconstructed vertices from 5 to 3. The estimated uncertainty is 1\% without $\ptlead$ or $\ptjet$ selection. The uncertainty varies up to 4\% for event with the $\ptlead$ or $\ptjet$ selection. The uncertainty for $Y^{\rm{jet}}$ is estimated to be 0--2\$ with varying event-scale selections.
%Pileup cut (multbins) -> (default pileup from the physics selection)
%Pileup cut (multbins) -> PileupMV (?)
The uncertainty from the primary vertex selection along the beam axis is estimated by varying the selection range of primary vertex from $|z_\mathrm{vtx}|<$ 8 to 6 cm. The narrower primary vertex selection allows one to test the acceptance effect on the measurement. The estimated uncertainty is 1--12\% with the varying event-scale selections. The uncertainty for $Y^{\rm{jet}}$ is estimated to be 1--8\%.

The uncertainty from the track selection is estimated by varying from the hybrid tracks to the other one optimized for particle identification that is called the global tracks. The selection criteria of the global tracks are almost identical to the hybrid tracks except for the requirement of at least one hit on the SPD. Due to the requirement, the quality of the global tracks is sensitive to the condition of the SPD, finally resulting a non-flat azimuthal distribution of charged particles with the selection. 
%The variation is achieved by changing the mandatory SPD requirement and the maximal threshold for chi-square of the track fit.
%https://github.com/alisw/AliRoot/blob/master/ANALYSIS/ESDfilter/macros/AddTaskESDFilter.C
The uncertainty origination from the variation of the track selections is estimated as 4\%. The uncertainty is measured by averaging for various transverse momentum ranges regardless of event-scale selections. The uncertainty for $Y^{\rm{jet}}$ is estimated to be 2--3\%.

The ZYAM procedure is implemented by finding a minimum yield in a given finding range. The uncertainty from the ZYAM procedure is estimated by varying the range from the $|\Delta\varphi|<\pi/$2 up to $|\Delta\varphi|<1.2$. The estimated uncertainty for track selection is 5.1\% by averaging the uncertainty for the whole transverse momentum bins and 2\% for 1$<\it{p}_{\rm{T}}<$2 GeV/$c$ tracks, which is not largely affected by the event-scale selection. The uncertainty for $Y^{\rm{jet}}$ is not considered due to negligible deviation compared with statistical fluctuation. The uncertainty from the jet contamination is estimated by varying the $\Delta\eta$ projection range to see how much the jet contamination varies, which is thought be small. The estimated uncertainty is 3--9\% with the varying event-scale selection. The uncertainty for $Y^{\rm{jet}}$ is not evaluated as the jet yield is measured.

The uncertainty from the event mixing intervals of primary vertex is estimated by varying the interval size from 2 to 1 cm. The estimated uncertainty is 1--16\% with the varying event-scale selection. The uncertainty for $Y^{\rm{jet}}$ is estimated to be 1\%. The uncertainty from the efficiency correction for charged track is estimated by comparing correlations functions of true particles with correlations functions of reconstructed tracks with the efficiency correction in simulation. The estimated uncertainty is 1--2.5\% regardless of the event-scale selection. The uncertainty for $Y^{\rm{jet}}$ is estimated to be 3\%.

### 2020-10-26 sec_results.tex
updates

\begin{figure}[h!]
	\centering
	\subfigure{ \includegraphics[width=0.47 \textwidth]{./figures/corr1.eps} }
	\subfigure{ \includegraphics[width=0.47 \textwidth]{./figures/corrmb.eps} }
	\caption{ Dihadron correlation functions as functions of $\Delta\eta$ and $\Delta\varphi$ in the high-multiplicity (0--0.1\%, left) and the minimum-bias events (0--100\%, right). The intervals of $\pttrig$ and $\ptassoc$ are equally $1 < \it{p}_{\rm{T}} < 2$ GeV/$c$. }
	\label{fig:PlotCorrMBHMT}
\end{figure}

@@

\begin{figure}[h!]
	\centering
	\includegraphics[width=0.9\linewidth]{./figures/Fig2_PlotDeltaPhi.eps}
	\caption{One-dimensional $\Delta\varphi$ distribution in the large $\Delta\eta$ projection for various transverse momentum intervals in each multiplicity class. The distributions in upper panels are measured with 0--100\% multiplicity class. The distribution in lower panels are measured with 0--0.1\% multiplicity class. Transverse momentum ranges of trigger particle and associated particle are $1<\pt<2$ (left), $2<\pt<3$ (middle) and $3<\pt<4$ GeV/$c$ (right), respectively. The model predictions are presented as colored lines. Blue line corresponds to $\pythiashoving$, orange line corresponds to $\pythiam$ and green line corresponds to $\epos$.}
	\label{fig:PlotDeltaPhi}
\end{figure}

@@

\begin{figure}[h!]
	\centering
	\subfigure{\includegraphics[width=0.99\textwidth]{./figures/Fig3_PlotRidgeYield.eps}}
	\caption{ Fully corrected near-side ridge yield as a function transverse momentum. The filled circles denote the measurement with ALICE. The CMS measurement~\cite{Khachatryan:2015lva} is represented by open blue box markers. The three lines show model predictions from $\pythiam$ (blue line), $\pythiashoving$ (orange line) and $\epos$ (green line).}
	\label{fig:PlotYSpect}
\end{figure}

@@

\subsection{Event-scale dependence of the ridge yield}
\begin{figure}[h!]
	\centering
	\subfigure{ \includegraphics[width=0.47 \textwidth]{./figures/corrlh.eps} }
	\subfigure{ \includegraphics[width=0.47 \textwidth]{./figures/corrjet.eps} }
	\caption{ Two-dimensional correlations function as a function of $\Delta\eta$ and $\Delta\varphi$ in top 0-0.1\% multiplicity class with the minimum $\ptlead$ (left) or $\ptjet$ (right) selection. The interval of $\pttrig$ and $\ptassoc$ is $1<\pt<2$ GeV/$c$. The minimum requirement for $\ptlead$ or $\ptjet$ is 9 or 10 GeV/$c$, respectively. }
	\label{fig:PlotCorrHMTSel}
\end{figure}

@@

\begin{figure}[h!]
	\centering
	\includegraphics[width=0.99\linewidth]{./figures/Fig5_PlotDeltaPhiESE.eps}
	\caption{ One-dimensional $\Delta\varphi$ distribution in the large $\Delta\eta$ with the minimum $\ptlead$(lower) or $\ptjet$(upper) selection for $1< \pttrig~\mathrm (\ptassoc) <2$ GeV/$c$ in the 0--0.1\% multiplicity class. The filled circles show the ALICE measurement. Model predictions are presented with a blue line for $\pythiam$, an orange line for $\pythiashoving$ and a green line for $\epos$.}
	\label{fig:PlotDeltaPhiESE}
\end{figure}

Figure~\ref{fig:PlotDeltaPhiESE} shows projected $\Delta\varphi$ distributions of the correlation functions in $1.6<|\Delta\eta|<1.8$ with the minimum $\ptlead$ (lower) and $\ptjet$ (upper) requirement. Even with the event-scale selection, the ridge is still visible at the near-side. The near-side yield increases as the threshold of $\ptjet$ increases compared to one measured in unbiased events, while the ridge yields for an increasing threshold of $\ptlead$ increase less than those of $\ptjet$. \iffalse The event-scale measurement with $\ptlead$ favors harder jets as a leading particle carries a large fraction of the momentum. In contrast, soft jets are favored for reconstructed jets. \fi The results are compared with $\pythiashoving$, $\pythiam$, and $\epos$ calculations. The near-side peaks are qualitatively reproduced by $\pythiashoving$ and $\epos$, while underestimated by $\pythiashoving$ and overestimated by $\epos$. On the other hand, $\pythiam$ does not show the near-side peak with the event-scale selections, while giving similar estimates for away-side yield as $\pythiashoving$.
%Both models describe the away-side yield with the $\ptjet$ selection and overestimate away-side yield with the $\ptlead$ selection.

\begin{figure}[h!]
	\centering
	\includegraphics[width=0.99\linewidth]{./figures/Fig6_RidgeYieldESE.eps}
	\caption{The ridge yield spectra with respect to the leading particle and jet selections. The filled circles show measurement with ALICE. Model predictions are compared to measurement as blue lines for $\pythiam$, orange lines for $\pythiashoving$ and green lines for $\epos$. Ratios of measured data to models are prepared for $\pythiashoving$ and $\epos$.}
	\label{fig:RidgeYield_ESE}
\end{figure}

@@

>>>>

\begin{figure}[h!]
	\centering
	\subfigure{ \includegraphics[width=0.47 \textwidth]{./figures/corr1.pdf} }
	\subfigure{ \includegraphics[width=0.47 \textwidth]{./figures/corrmb.pdf} }
	\caption{ Dihadron correlation functions as functions of $\Delta\eta$ and $\Delta\varphi$ in the high-multiplicity (0--0.1\%, left) and the minimum-bias events (0--100\%, right). The intervals of $\pttrig$ and $\ptassoc$ are equally $1 < \it{p}_{\rm{T}} < 2$ GeV/$c$. }
	\label{fig:PlotCorrMBHMT}
\end{figure}

@@

\begin{figure}[h!]
	\centering
	\includegraphics[width=0.9\linewidth]{./figures/Fig2_PlotDeltaPhi.pdf}
	\caption{One-dimensional $\Delta\varphi$ distribution in the large $\Delta\eta$ projection for various transverse momentum intervals in each multiplicity class. The distributions in upper panels are measured with 0--100\% multiplicity class. The distribution in lower panels are measured with 0--0.1\% multiplicity class. Transverse momentum ranges of trigger particle and associated particle are $1<\pt<2$ (left), $2<\pt<3$ (middle) and $3<\pt<4$ GeV/$c$ (right), respectively. The model predictions are presented as colored lines. Blue line corresponds to $\pythiashoving$, orange line corresponds to $\pythiam$ and green line corresponds to $\epos$.}
	\label{fig:PlotDeltaPhi}
\end{figure}

@@

\begin{figure}[h!]
	\centering
	\subfigure{\includegraphics[width=0.99\textwidth]{./figures/Fig3_PlotRidgeYield.pdf}}
	\caption{ Fully corrected near-side ridge yield as a function transverse momentum. The filled circles denote the measurement with ALICE. The CMS measurement~\cite{Khachatryan:2015lva} is represented by open blue box markers. The three lines show model predictions from $\pythiam$ (blue line), $\pythiashoving$ (orange line) and $\epos$ (green line).}
	\label{fig:PlotYSpect}
\end{figure}

@@

\subsection{Event-scale dependence of the ridge yield}
\begin{figure}[h!]
	\centering
	\subfigure{ \includegraphics[width=0.47 \textwidth]{./figures/corrlh.pdf} }
	\subfigure{ \includegraphics[width=0.47 \textwidth]{./figures/corrjet.pdf} }
	\caption{ Two-dimensional correlations function as a function of $\Delta\eta$ and $\Delta\varphi$ in top 0-0.1\% multiplicity class with the minimum $\ptlead$ (left) or $\ptjet$ (right) selection. The interval of $\pttrig$ and $\ptassoc$ is $1<\pt<2$ GeV/$c$. The minimum requirement for $\ptlead$ or $\ptjet$ is 9 or 10 GeV/$c$, respectively. }
	\label{fig:PlotCorrHMTSel}
\end{figure}

@@

\begin{figure}[h!]
	\centering
	\includegraphics[width=0.99\linewidth]{./figures/Fig5_PlotDeltaPhiESE.pdf}
	\caption{ One-dimensional $\Delta\varphi$ distribution in the large $\Delta\eta$ with the minimum $\ptlead$(lower) or $\ptjet$(upper) selection for $1< \pttrig~\mathrm (\ptassoc) <2$ GeV/$c$ in the 0--0.1\% multiplicity class. The filled circles show the ALICE measurement. Model predictions are presented with a blue line for $\pythiam$, an orange line for $\pythiashoving$ and a green line for $\epos$.}
	\label{fig:PlotDeltaPhiESE}
\end{figure}

Figure~\ref{fig:PlotDeltaPhiESE} shows projected $\Delta\varphi$ distributions of the correlation functions in $1.6<|\Delta\eta|<1.8$ with the minimum $\ptlead$ (lower) and $\ptjet$ (upper) requirement. Even with the event-scale selection, the ridge is still visible at the near-side. The near-side yield increases as the threshold of $\ptjet$ increases compared to one measured in unbiased events, while the ridge yields for an increasing threshold of $\ptlead$ increase less than those of $\ptjet$. The results are compared with $\pythiashoving$, $\pythiam$, and $\epos$ calculations. The near-side peaks are qualitatively reproduced by $\pythiashoving$ and $\epos$, while underestimated by $\pythiashoving$ and overestimated by $\epos$. On the other hand, $\pythiam$ does not show the near-side peak with the event-scale selections, while giving similar estimates for away-side yield as $\pythiashoving$.
%Both models describe the away-side yield with the $\ptjet$ selection and overestimate away-side yield with the $\ptlead$ selection.

\begin{figure}[h!]
	\centering
	\includegraphics[width=0.99\linewidth]{./figures/Fig6_RidgeYieldESE.pdf}
	\caption{The ridge yield spectra with respect to the leading particle and jet selections. The filled circles show measurement with ALICE. Model predictions are compared to measurement as blue lines for $\pythiam$, orange lines for $\pythiashoving$ and green lines for $\epos$. Ratios of measured data to models are prepared for $\pythiashoving$ and $\epos$.}
	\label{fig:RidgeYield_ESE}
\end{figure}

@@

\begin{figure}[h!]
	\centering
	\includegraphics[width=0.99\linewidth]{./figures/Fig9_JetYieldESE.pdf}
	\caption{The jet yield spectra with respect to the leading particle (left) and jet selections (right). The filled circles show measurement with ALICE. Model predictions are compared to measurement as blue lines for $\pythiam$, orange lines for $\pythiashoving$ and green lines for $\epos$.}
	\label{fig:RidgeYield_ESE}
\end{figure}

Jet yield has been measured as a function of minimum $\ptlead$ and $\ptjet$ threshold to further discuss ridge yields and jet yields.
%quantify the trend of the jet yield.
$\epos$ provides comparable estimates for jet yields, while $\pythiam$ and $\pythiashoving$ overestimate jet yields for both selections. Increasing trend of jet yield as a function of minimum $\ptlead$ and saturating trend of jet yield as a function of minimum $\ptjet$ have been observed and estimated by models. Jet yield measured with $\ptlead>$20~GeV/$c$ is comparable with the one measured with $\ptjet>$10~GeV/$c$, where ridge yields with corresponding selections are also comparable.
